\chapter{\CBC}
\label{cha:coincbc}
\hypertarget{cha:coincbc}{}

\CBC (COIN-OR Branch and Cut) is an open-source mixed integer programming solver working with the COIN-OR LP solver \textsc{CLP} and the COIN-OR Cut generator library \textsc{Cgl}.
The code has been written primarily by John J. Forrest.

For more information we refer to the website of \CBC, \textsc{CGL}, and \textsc{CLP}:
\url{https://projects.coin-or.org/Cbc}, \url{https://projects.coin-or.org/Cgl}, \url{https://projects.coin-or.org/Clp}.
Most of the \CBC documentation in the section was copied from the help in the \CBC standalone version.

The \CBC link in \GAMS supports continuous, binary, integer, semicontinuous, semiinteger variables, special ordered sets of type 1 and 2, and branching priorities (see chapter 17.1 of the \GAMS User's Guide).
% Quadratic objective functions are not supported yet.

\section{Usage}

The following statement can be used inside your \GAMS program to specify using \CBC
\begin{verbatim}
  Option LP = CBC;     { or MIP or RMIP }
\end{verbatim}

The above statement should appear before the Solve statement.
If \CBC was specified as the default solver during \GAMS installation, the above statement is not necessary.

\subsection{Specification of Options}

The \GAMS/\CBC options file consists of one option or comment per line.
An asterisk (*) at the beginning of a line causes the entire line to be ignored.
Otherwise, the line will be interpreted as an option name and value separated by any amount of white space (blanks or tabs).
Following is an example options file \texttt{cbc.opt}.
\begin{verbatim}
  cuts root
  perturbation off
\end{verbatim}
It will cause \CBC to use cut generators only in the root node and turns off the perturbation of the LP relaxation.

\GAMS/\CBC currently does not support the \GAMS Branch-and-Cut-and-Heuristic (BCH) Facility.
If you need to use \GAMS/\CBC with BCH, please consider to use a \GAMS system of version $\leq 23.3$, available at \url{http://www.gams.com/download/download_old.htm}.

% \GAMS/\CBC supports the \GAMS Branch-and-Cut-and-Heuristic (BCH) Facility.
% The \GAMS BCH facility automates all major steps necessary to define, execute, and control the use of user defined routines within the framework of general purpose MIP codes.
% Currently supported are user defined cut generators and heuristics.
% Please see the BCH documentation at \texttt{http://www.gams.com/docs/bch.htm} for further information.

\section{Options}

Among all \CBC options, the following \GAMS parameters are currently supported in \CBC:
\hyperlink{reslim}{reslim}, \hyperlink{iterlim}{iterlim}, \hyperlink{nodlim}{nodlim}, \hyperlink{optca}{optca}, \hyperlink{optcr}{optcr}, \hyperlink{increment}{cheat}, \hyperlink{cutoff}{cutoff}, \hyperlink{threads}{threads} (experimental on Windows systems).

There are many parameters which can affect the performance the \CBC{}s Branch and Cut Algorithm.
First just try with default settings and look carefully at the log file.
Did cuts help? Did they take too long? Look at the output to see which cuts were effective and then do some tuning (see the option \hyperlink{cuts}{cuts}).
If the \hyperlink{preprocess}{preprocessing} reduced the size of the problem or strengthened many coefficients then it is probably wise to leave it on.
Switch off \hyperlink{heuristics}{heuristics} which did not provide solutions.
The other major area to look at is the search.
Hopefully good solutions were obtained fairly early in the search so the important point is to select the best variable to branch on.
See whether strong branching did a good job -- or did it just take a lot of iterations?
Adjust the options \hyperlink{strongbranching}{strongbranching} and \hyperlink{trustpseudocosts}{trustpseudocosts}.

In the following, we summarize all available \CBC options.
\input{optcbc_s}

In the following, we give a detailed description of all available \CBC options.
\input{optcbc_a}

%\bibliographystyle{plain}
%\bibliography{coinlibd}
%\renewcommand{\bibname}{CBC References}
%\input{cbc.bbl}

\chapterend