\chapter{\COUENNE}

COIN-OR \COUENNE (\textbf{C}onvex \textbf{O}ver and \textbf{U}nder \textbf{En}velopes for \textbf{N}onlinear \textbf{E}stimation) is an open-source solver for nonconvex mixed-integer nonlinear programming (MINLPs).
The code has been developed originally in a cooperation of Carnegie Mellon University and IBM Research, and now at Clemson University.
The COIN-OR project leader for \COUENNE is Pietro Belotti.

\COUENNE solves convex and nonconvex MINLPs by an LP based spatial branch-and-bound algorithm. % that is similar to the algorithm used in \textsc{BARON}.
The implementation extends \BONMIN by routines to compute valid linear outer approximations for nonconvex problems and methods for bound tightening and branching on nonlinear variables.
\COUENNE uses \IPOPT to solve NLP subproblems.

For more information on the algorithm we refer to \cite{Be09,BeLeLiMaWa08} and the \COUENNE web site \url{https://projects.coin-or.org/Couenne}.
Most of the \COUENNE documentation in this section is taken from the \COUENNE manual~\cite{CouenneManual}.

\COUENNE can handle mixed-integer nonlinear programming models which functions can be nonconvex, but should be twice continuously differentiable. Further, an algebraic description of the model need to be made available, which makes the use of some \GAMS functions and user-specified external functions impossible.
The \COUENNE link in \GAMS supports continuous, binary, and integer variables, but no special ordered sets, semi-continuous or semi-integer variables (see chapter 17.1 of the \GAMS User's Guide).

%If \GAMS/\COUENNE is called for a linear model, the interface directly calls \CBC.

\section{Usage}

The following statement can be used inside your \GAMS program to specify using \COUENNE
\begin{verbatim}
  Option MINLP = COUENNE;     { or LP, RMIP, MIP, DNLP, NLP, RMINLP, QCP, RMIQCP, MIQCP }
\end{verbatim}

The above statement should appear before the Solve statement.
If \COUENNE was specified as the default solver during \GAMS installation, the above statement is not necessary.

\subsection{Specification of Options}

A \COUENNE option file contains \IPOPT, \BONMIN, and \COUENNE options, for clarity all \BONMIN options should be preceded with the prefix ``\texttt{bonmin.}'' and all \COUENNE options should be preceded with the prefix ``\texttt{couenne.}''.
All \IPOPT and many \BONMIN options are available in \COUENNE, please refer to the Sections~\ref{sub:ipoptoptions} and \ref{sub:bonminalloptions} for a detailed description.
The scheme to name option files is the same as for all other \GAMS solvers.
Specifying \texttt{optfile=1} let \GAMS/\COUENNE read \texttt{couenne.opt}, \texttt{optfile=2} corresponds to \texttt{couenne.op2}, and so on.
The format of the option file is the same as for \IPOPT (see Section~\ref{sub:ipoptoptionspec}).

\GAMS/\COUENNE understands currently the following \GAMS parameters: \texttt{reslim} (time limit), \texttt{nodlim} (node limit), \texttt{cutoff}, \texttt{optca} (absolute gap tolerance), and \texttt{optcr} (relative gap tolerance).
One can set them either on the command line, e.g. \verb+nodlim=1000+, or inside your \GAMS program, e.g. \verb+Option nodlim=1000;+.
Further the option \texttt{threads} can be used to control the number of threads used in the linear algebra routines of \IPOPT, see Section~\ref{sec:ipoptlinearsolver} in Chapter~\ref{cha:ipopt} for details.

\section{Detailed Options Description}
\label{sub:couenneoptions}

In the following we give a detailed list of options available for \COUENNE solely.
The value on the right denotes the default value.
Note that options specific to \IPOPT and \BONMIN are not listed her, see Sections \ref{sub:bonminalloptions} and \ref{sub:ipoptoptions} instead.

\input{optcouenne_a}

\bibliographystyle{plain}
%\bibliography{coinlibd}
%\renewcommand{\bibname}{Couenne References}
\input{couenne.bbl}

\chapterend