\subsection{Detailed Descriptions of CoinGlpk Options}

\begin{description}

\item[\label{glpkstartalg}\hypertarget{glpkstartalg}
{\textbf{startalg (\slshape{string})}}]\hspace{1.0in}

This option determines whether a primal or dual simplex algorithm should be used to solve an LP or the root node of a MIP.

\textsl{(default = primal)}
\begin{itemize}
\item[primal] 
Let GLPK use a primal simplex algorithm.
\item[dual] 
Let GLPK use a dual simplex algorithm.
\end{itemize}

\item[\label{glpkscaling}\hypertarget{glpkscaling}
{\textbf{scaling (\slshape{string})}}]\hspace{1.0in}

This option determines the method how the constraint matrix is scaled.
Note that scaling is only applied when the \hyperlink{presolve}{presolver} is turned off, which is on by default.

\textsl{(default = meanequilibrium)}
\begin{itemize}
\item[off] 
Turn off scaling.
\item[equilibrium] 
Let GLPK use an equilibrium scaling method.
\item[mean] 
Let GLPK use a geometric mean scaling method.
\item[meanequilibrium] 
Let GLPK use first a geometric mean scaling, then an equilibrium scaling.
\end{itemize}

\item[\label{pricing}\hypertarget{pricing}
{\textbf{pricing (\slshape{string})}}]\hspace{1.0in}

Sets the pricing method for both primal and dual simplex.

\textsl{(default = steepestedge)}
\begin{itemize}
\item[textbook] 
Use a textbook pricing rule.
\item[steepestedge] 
Use a steepest edge pricing rule.
\end{itemize}

\item[\label{factorization}\hypertarget{factorization}
{\textbf{factorization (\slshape{string})}}]\hspace{1.0in}

Sets the method for the LP basis factorization.

If you observe that GLPK reports numerical instabilities than you could try to use a more stable factorization method.

\textsl{(default = forresttomlin)}
\begin{itemize}
\item[forresttomlin] 
Does a LU factorization followed by Forrest-Tomlin updates.
This method is fast, but less stable than others.
\item[bartelsgolub] 
Does a LU factorization followed by a Schur complement and Bartels-Golub updates.
This method is slower than Forrest-Tomlin, but more stable.
\item[givens] 
Does a LU factorization followed by a Schur complement and Givens rotation updates.
This method is slower than Forrest-Tomlin, but more stable.
\end{itemize}

\item[\label{initbasis}\hypertarget{initbasis}
{\textbf{initbasis (\slshape{string})}}]\hspace{1.0in}

Sets the method that computes the initial basis.
Setting this option has only effect if the \hyperlink{presolve}{presolver} is turned off, which is on by default.

\textsl{(default = advanced)}
\begin{itemize}
\item[standard] 
Uses the standard initial basis of all slacks.
\item[advanced] 
Computes an advanced initial basis.
\item[bixby] 
Uses Bixby's initial basis.
\end{itemize}

\item[\label{glpktol_dual}\hypertarget{glpktol_dual}
{\textbf{tol\_dual (\slshape{real})}}]\hspace{1.0in}

Absolute tolerance used to check if the current basis solution is dual feasible.
% (Glpk manual: Do not change this parameter without detailed understanding its purpose.)

\textsl{(default = 1e-7)}

\item[\label{glpktol_primal}\hypertarget{glpktol_primal}
{\textbf{tol\_primal (\slshape{real})}}]\hspace{1.0in}

Relative tolerance used to check if the current basis solution is primal feasible.
% (Glpk manual: Do not change this parameter without detailed understanding its purpose.)

\textsl{(default = 1e-7)}

\item[\label{glpktol_integer}\hypertarget{glpktol_integer}
{\textbf{tol\_integer (\slshape{real})}}]\hspace{1.0in}

Absolute tolerance used to check if the current basis solution is integer feasible.
% (Glpk manual: Do not change this parameter without detailed understanding its purpose.)

\textsl{(default = 1e-5)}

\item[\label{backtracking}\hypertarget{backtracking}
{\textbf{backtracking (\slshape{string})}}]\hspace{1.0in}

Determines which method to use for the backtracking heuristic.

\textsl{(default = bestprojection)}
\begin{itemize}
\item[depthfirst] 
Let GLPK use a depth first search.
\item[breadthfirst] 
Let GLPK use a breadth first search.
\item[bestprojection] 
Let GLPK use a best projection heuristic.
\end{itemize}

\item[\label{glpkpresolve}\hypertarget{glpkpresolve}
{\textbf{presolve (\slshape{integer})}}]\hspace{1.0in}

Determines whether the LP presolver should be used.

\textsl{(default = 1)}
\begin{itemize}
\item[0] 
Turns off the LP presolver.
\item[1] 
Turns on the LP presolver.
\end{itemize}

\item[\label{glpkcuts}\hypertarget{glpkcuts}
{\textbf{cuts (\slshape{integer})}}]\hspace{1.0in}

Determines which cuts generator to use: none, all, or user-defined

\textsl{(default = 0)}
\begin{itemize}
\item[-1] .
Turn off all cut generators
\item[0] .
Turn on or off each cut generators separately
\item[1] .
Turn on all cut generators
\end{itemize}

\item[\label{glpkcovercuts}\hypertarget{glpkcovercuts}
{\textbf{covercuts (\slshape{integer})}}]\hspace{1.0in}

Whether to enable cover cuts.

\textsl{(default = 1)}
\begin{itemize}
\item[0] .
Turn off cover cuts
\item[1] .
Turn on cover cuts
\end{itemize}

\item[\label{glpkcliquecuts}\hypertarget{glpkcliquecuts}
{\textbf{cliquecuts (\slshape{integer})}}]\hspace{1.0in}

Whether to enable clique cuts.

\textsl{(default = 1)}
\begin{itemize}
\item[0] .
Turn off clique cuts
\item[1] .
Turn on clique cuts
\end{itemize}

\item[\label{glpkgomorycuts}\hypertarget{glpkgomorycuts}
{\textbf{gomorycuts (\slshape{integer})}}]\hspace{1.0in}

Whether to enable Gomorys mixed-integer linear cuts.

\textsl{(default = 1)}
\begin{itemize}
\item[0] .
Turn off gomory cuts
\item[1] .
Turn on gomory cuts
\end{itemize}

\item[\label{glpkmircuts}\hypertarget{glpkmircuts}
{\textbf{mircuts (\slshape{integer})}}]\hspace{1.0in}

Whether to enable mixed-integer rounding cuts.

\textsl{(default = 0)}
\begin{itemize}
\item[0] .
Turn off mir cuts
\item[1] .
Turn on mir cuts
\end{itemize}


\item[\label{reslim_fixedrun}\hypertarget{reslim_fixedrun}
{\textbf{reslim\_fixedrun (\slshape{real})}}]\hspace{1.0in}

Maximum time in seconds for solving the MIP with fixed discrete variables.

\textsl{(default = 1000)}

\item[\label{noiterlim}\hypertarget{noiterlim}
{\textbf{noiterlim (\slshape{integer})}}]\hspace{1.0in}

Allows to switch off the \hyperlink{iterlim}{simplex iteration limit}.
You can remove the limit on the simplex iterations by setting the \hyperlink{noiterlim}{noiterlim} option.

\textsl{(default = 0)}
\begin{itemize}
\item[0] 
Keeps simplex iteration limit.
\item[1] 
Turns off simplex iteration limit.
\end{itemize}

\item[\label{glpknames}\hypertarget{glpknames}
{\textbf{names (\slshape{integer})}}]\hspace{1.0in}

This option causes GAMS names for the variables and equations to be loaded into Glpk.
These names will then be used for error messages, log entries, and so forth.
Turing names off may help if memory is very tight.

\textsl{(default = 0)}
\begin{itemize}
\item[0] .
Do not load variable and equation names.
\item[1] .
Load variable and equation names.
\end{itemize}

\item[\label{glpksolvefinal}\hypertarget{glpksolvefinal}
{\textbf{solvefinal (\slshape{integer})}}]\hspace{1.0in}

Sometimes the solution process after the branch-and-cut that solves the problem with fixed discrete variables takes a long time and the user is interested in the primal values of the solution only.
In these cases, this option can be used to turn this final solve off.
Without the final solve no proper marginal values are available and only zeros are returned to GAMS.

\textsl{(default = 1)}
\begin{itemize}
\item[0] .
Do not solve the fixed problem
\item[1] .
Solve the fixed problem and return duals
\end{itemize}

\item[\label{glpkreslim}\hypertarget{glpkreslim}
{\textbf{reslim (\slshape{real})}}]\hspace{1.0in}

Maximum time in seconds.

\textsl{(default = GAMS reslim)}

\item[\label{glpkiterlim}\hypertarget{glpkiterlim}
{\textbf{iterlim (\slshape{integer})}}]\hspace{1.0in}

Maximum number of simplex iterations.

\textsl{(default = GAMS iterlim)}

\item[\label{glpkoptcr}\hypertarget{glpkoptcr}
{\textbf{optcr (\slshape{real})}}]\hspace{1.0in}

Relative optimality criterion for a MIP.
The search is stoped when the relative gap between the incumbent and the bound given by the LP relaxation is smaller than this value.

\textsl{(default = GAMS optcr)}

\item[\label{glpkwritemps}\hypertarget{glpkwritemps}
{\textbf{writemps (\slshape{string})}}]\hspace{1.0in}

Write an MPS problem file.
The parameter value is the name of the MPS file.

\end{description}
