\chapter{Optimization Services (OS)}

COIN-OR \OS (\textbf{O}ptimization \textbf{S}ervices) is an initiative to provide a set of standards for representing optimization instances, results, solver options, and communication between clients and solvers in a distributed environment using Web Services.
The code has been written primarily by Horand Gassmann, Jun Ma, and Kipp Martin.
Kipp Martin is the COIN-OR project leader for \OS.

For more information we refer to the web sites \url{http://www.optimizationservices.org} and \url{https://projects.coin-or.org/OS}, the \OS manual~\cite{Ma2005}, and the papers~\cite{FourerMaMartin2009,FourerMaMartin2010,OSManual}.

With the \OS link in \GAMS, you can send your instance to an Optimization Services Server for remote solving.

\OS supports continuous, binary, integer, semicontinuous, and semiinteger variables and linear and nonlinear equations.
Special ordered sets and indicator constraints are currently not supported.
Initial values are currently not supported by the \GAMS/\OS link.

\section{Usage}

The following statement can be used inside your \GAMS program to specify using \OS
\begin{verbatim}
  Option MINLP = OS;     { or LP, RMIP, MIP, DNLP, NLP, RMINLP, QCP, RMIQCP, MIQCP }
\end{verbatim}

The above statement should appear before the Solve statement.

By default, for a given instance of a \GAMS model, nothing happens.
To solve an instance remotely, you have to specify the URL of an Optimization Services Server via the option \texttt{service}.
Usually, the server chooses an appropriate solver for your instance, depending on their availability on the server.
A fully equipped server chooses
\textsc{CLP} for continuous linear models (LP and RMIP),
\IPOPT for continuous nonlinear models (NLP, DNLP, RMINLP, QCP, RMIQCP),
\CBC for mixed-integer linear models (MIP), and
\BONMIN for mixed-integer nonlinear models (MIQCP, MINLP).
An easy way to influence the choice of the solver on the server is the \texttt{solver} option.

Further options can be provided in an OSoL (Optimization Services Options Language) file, which is specified via the the \texttt{readosol} option.
An example OSoL file looks like
\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<osol xmlns="os.optimizationservices.org" xmlns:xs="http://www.w3.org/2001/XMLSchema"
      xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance"
      xsi:schemaLocation="os.optimizationservices.org
                          http://www.optimizationservices.org/schemas/2.0/OSoL.xsd">
<optimization>
  <solverOptions numberOfSolverOptions="3">
    <solverOption name="cuts" solver="cbc" value="off" />
    <solverOption name="max_active_nodes" solver="symphony"  value="2" />
    <solverOption name="max_iter" solver="ipopt" type="integer" value="2000"/>
  </solverOptions>
</optimization>
</osol>
\end{verbatim}
It specifies that if \CBC is used, then cutting planes are disabled,
if \textsc{SYMPHONY} is used, then at most 2 nodes should be active,
and if \IPOPT is used, then a limit of 2000 iterations is imposed.

By default, the call to the server is a \emph{synchronous} call.
The \GAMS process will wait for the result and then display the result.
This may not be desirable when solving large optimization models.
In order to use the remote solver service in an \emph{asynchronous} fashion, one can make use of the \GAMS Grid Computing Facility, see Appendix I in the \GAMS manual.

\section{Detailed Options Descriptions}

\input{optosd_a}

\bibliographystyle{plain}
%\bibliography{coinlibd}
%\renewcommand{\bibname}{OS References}
\input{os.bbl}

\chapterend
